### 2023-11-09 manuscript/manuscript.Rmd
log10 scale the MF plausibility rank axes in Figure 2

```{r figure-2-kegg-mf-selection,fig.height=4,fig.cap='Molecular formula plausibility ($P_{MF}$) rankings of KEGG compound molecular formulas. The $P_{MF}$ rankings were based on the monoisotopic masses of 6745 valid KEGG compound molecular formulas for which molecular formulas were generated using a mass error of $\\pm$ 4 ppm.'}
tar_read(KEGG_compound_MF_ranks_mass_plot) +
  tar_read(KEGG_compound_MF_ranks_n_plot)
```

>>>>

```{r figure-2-kegg-mf-selection,fig.height=4,fig.cap='Molecular formula plausibility ($P_{MF}$) rankings of KEGG compound molecular formulas. The $P_{MF}$ rankings were based on the monoisotopic masses of 6744 valid KEGG compound molecular formulas for which molecular formulas were generated using a mass error of $\\pm$ 4 ppm.'}
tar_read(KEGG_compound_MF_ranks_mass_plot) +
  tar_read(KEGG_compound_MF_ranks_n_plot)
```
